Using a Two-Layer Neural Network and Physicochemical Properties to Classify Glass for Forensic Analysis

### 2017-06-28 Paper/paper.tex
edits

\section{Introduction}
\label{sec2}
An overview of the project and an outline of the report (I like to write intro after I finish a project).

\subsection{Literature Review}
\label{sec2.1}
The dataset we will use for this analysis was initially employed in Evett and Spiehler's paper \emph{Rule Induction in Forensic Science} (1987) \cite{evett1987}. They recognized the usefulness to a forensic crime lab of classifying glass fragments based on refractive index and chemical composition. This would, for example, allow the lab to ascertain whether samples gathered on a suspect?s clothing came from a window, potentially indicating they had broken it, or from another source, like a broken bottle.

>>>>

\section{Literature Review}
\label{sec2}
The dataset we will use for this analysis was initially employed in Evett and Spiehler's paper \emph{Rule Induction in Forensic Science} (1987) \cite{evett1987}. They recognized the usefulness to a forensic crime lab of classifying glass fragments based on refractive index and chemical composition. This would, for example, allow the lab to ascertain whether samples gathered on a suspect?s clothing came from a window, potentially indicating they had broken it, or from another source, like a broken bottle.
